Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-12-22 writing/CONUS_AOD.Rmd
Report the last-modifed date for AERONET.
Closes #30 (per conversation).
Simplified some inline code.
Renamed lots of variables.

@@

```{r table_cv_results, echo=FALSE}
kbl(pretty.table.numbers(tar_read(cv_summary_table)[1, -"Year"]), align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:12, width = "1.1cm")
```

@@

```{r stratified, echo=FALSE}
dt <- copy(tar_read(initial_cv)$mDT_wPred)
```

@@

```{r strata_year, echo=FALSE, eval=TRUE}
kbl(pretty.table.numbers(tar_read(cv_summary_table)[-1]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

```{r shap_rank, echo=FALSE}
# what do the SHAPs tell us?
tar_load(initial_cv)
shaps <- initial_cv$"shap_score"
# sort by importance
df_shap <- data.frame(meanabsshap = round(sort(sapply(abs(shaps), mean), decreasing = TRUE), 4))
kbl(df_shap, col.names = "Mean |SHAP|") %>% row_spec(0, bold=TRUE)
# df_shap$variable <- row.names(df_shap)
# ft_shap <- flextable(df_shap[, c(2, 1)])
# ft_shap <- set_header_labels(ft_shap, list(variable = "Variable", meanabsshap = "Mean Absolute SHAP"))
# ft_shap
```
Summary visualization of SHAP contributions

```{r shap_summary, echo=FALSE, dev='png', dpi=300, eval=FALSE}
shap_long <- shap.prep(shap_contrib = initial_cv$shap_score,
                       X_train = initial_cv$mDT_wPred[, names(initial_cv_l2$shap_score), with = F])
# **SHAP summary plot**
shap.plot.summary(shap_long)
```

@@

```{r pred.map.median.mse, echo = F}
pred.map(
    tar_read(T.median.mse.map.data)$pred, tar_read(pred_grid),
    bg.sf = get_conus(), color.scale.name = "AOD",
    limits = list(lon = c(-107, Inf), lat = c(-Inf, 37)),
    quantile.cap = .99)
```

This map shows a tile on `r tar_read(T.median.mse.map.data)$date`.

@@

```{r pred.map.balitmore, echo = F}
pred.map(
    tar_read(T.baltimore.map.data), tar_read(pred_grid),
    bg.sf = get_conus(), color.scale.name = "AOD")
```

>>>>

We used a copy of the AERONET observations that was last modified `r lubridate::as_date(tz = "UTC", file.mtime(tar_read(aer_orig_obs_path)))`.

@@

```{r table_cv_results, echo=FALSE}
kbl(pretty.table.numbers(tar_read(cv.summary)[1, -"Year"]), align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:12, width = "1.1cm")
```

@@

```{r stratified, echo=FALSE}
dt <- copy(tar_read(cv)$mDT_wPred)
```

@@

```{r strata_year, echo=FALSE, eval=TRUE}
kbl(pretty.table.numbers(tar_read(cv.summary)[-1]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

```{r shap_rank, echo=FALSE}
# what do the SHAPs tell us?
tar_load(cv)
shaps <- cv$"shap_score"
# sort by importance
df_shap <- data.frame(meanabsshap = round(sort(sapply(abs(shaps), mean), decreasing = TRUE), 4))
kbl(df_shap, col.names = "Mean |SHAP|") %>% row_spec(0, bold=TRUE)
# df_shap$variable <- row.names(df_shap)
# ft_shap <- flextable(df_shap[, c(2, 1)])
# ft_shap <- set_header_labels(ft_shap, list(variable = "Variable", meanabsshap = "Mean Absolute SHAP"))
# ft_shap
```
Summary visualization of SHAP contributions

```{r shap_summary, echo=FALSE, dev='png', dpi=300, eval=FALSE}
shap_long <- shap.prep(shap_contrib = cv$shap_score,
                       X_train = cv$mDT_wPred[, names(cv$shap_score), with = F])
# **SHAP summary plot**
shap.plot.summary(shap_long)
```

@@

```{r pred.map.median.mse, echo = F}
pred.map(
    tar_read(median.mse.map.data)$pred, tar_read(pred.grid),
    bg.sf = get_conus(), color.scale.name = "AOD",
    limits = list(lon = c(-107, Inf), lat = c(-Inf, 37)),
    quantile.cap = .99)
```

This map shows a tile on `r tar_read(median.mse.map.data)$date`.

@@

```{r pred.map.baltimore, echo = F}
pred.map(
    tar_read(baltimore.map.data), tar_read(pred.grid),
    bg.sf = get_conus(), color.scale.name = "AOD")
```
